Automated topic naming to support analysis of software maintenance activities

### 2010-08-17 icse/icse2011.tex
code and figures for properly plotting timelines. Matplotlib is overly configurable.
Signed-off-by: Neil Ernst <neil@neilernst.net>

\begin{figure*}
  \centering
 \includegraphics[width=.75\textwidth]{figures/unsupervised-bar}
 \caption{ROC values for each NFR, per project and wordlist.}
%\todo[inline]{this is too tiny in print}

@@

\begin{figure*}[ht]
\centering
\subfigure[MySQL]{
\includegraphics[width=0.4\textwidth]{figures/mysql-supervised}
\label{fig:subfig1}
}
\subfigure[MaxDB]{
\includegraphics[width=0.4\textwidth]{figures/maxdb-supervised}
\label{fig:subfig2}
}
\label{fig:best-learn-per-tag}
\caption[]{ROC value (black) for the best learner per label, compared with ZeroR accuracy values (grey).
\todo[inline]{better discussion and graphical legend would be nice}
}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\subfigure[MySQL]{
\includegraphics[width=0.4\textwidth]{figures/multi-label-results-mysql}
\label{fig:subfig3}
}
\subfigure[MaxDB]{
\includegraphics[width=0.4\textwidth]{figures/multi-label-results-maxdb}
\label{fig:subfig4}
}
\label{fig:mulan}
\caption[]{MySQL and MaxDB macro (grey) and micro (black) ROC results per multi-label learner.
\todo[inline]{better discussion and graphical legend would be nice}
}
\end{figure*}

@@

\begin{figure*}
  \centering
  % hi-res version
  %\includegraphics[height=.55\textheight]{maxdb-time-smear-plot-Equal}
  \includegraphics[height=.55\textheight]{figures/small-maxdb-time-smear-plot-Equal}
  % \includegraphics[height=.57\textheight]{small-maxdb-time-smear-plot-Equal}
  \caption{MaxDB 7.500: Labelled topics related to non-functional software qualities plotted over time, continuous topics are trends that occur across time}
  \label{fig:maxdb}
\end{figure*}

\begin{figure*}%[h]
  \centering
  % hi-res version
  %\includegraphics[width=.97\textwidth]{mysql-time-smear-plot-Equal}
  %\includegraphics[width=.97\textwidth]{small-mysql-time-smear-plot-Equal}
  \includegraphics[width=.97\textwidth]{figures/mysql-timeline}
  \caption{MySQL 3.23:NFRs over time. Topic frequency is mapped to alpha (transparency) value.}
  \label{fig:mysql}
\end{figure*}

>>>>

\begin{figure*}
  \centering
 \includegraphics[width=.85\textwidth]{figures/unsupervised-bar}
 \caption{ROC values for each NFR, per project and wordlist.}
%\todo[inline]{this is too tiny in print}

@@

\begin{figure*}[ht]
\centering
\subfigure[MySQL]{
\includegraphics[width=0.4\textwidth]{figures/mysql-supervised}
\label{fig:subfig1}
}
\subfigure[MaxDB]{
\includegraphics[width=0.4\textwidth]{figures/maxdb-supervised}
\label{fig:subfig2}
}
\label{fig:best-learn-per-tag}
\caption[]{ROC value for the best learner per label, compared with ZeroR accuracy values.  Possible values range from 0--1.
\todo[inline]{better discussion}
}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\subfigure[MySQL]{
\includegraphics[width=0.4\textwidth]{figures/multi-label-results-mysql}
\label{fig:subfig3}
}
\subfigure[MaxDB]{
\includegraphics[width=0.4\textwidth]{figures/multi-label-results-maxdb}
\label{fig:subfig4}
}
\label{fig:mulan}
\caption[]{MySQL and MaxDB macro (grey) and micro (black) ROC results per multi-label learner. Possible values range from 0--1.
\todo[inline]{better discussion}% and graphical legend would be nice}
}
\end{figure*}

@@

\begin{figure*}
  \centering
  % hi-res version
  %\includegraphics[height=.55\textheight]{maxdb-time-smear-plot-Equal}
  \includegraphics[width=\textwidth]{figures/maxdb-timeline}
  % \includegraphics[height=.57\textheight]{small-maxdb-time-smear-plot-Equal}
 % \caption{MaxDB 7.500: Labelled topics related to non-functional software qualities plotted over time, continuous topics are trends that occur across time}
  \caption{MaxDB 7.500: NFRs over time. Topic frequency relative to that quality is mapped to alpha (transparency) value.}
 \label{fig:maxdb}
\end{figure*}

\begin{figure*}%[h]
  \centering
 %\includegraphics[width=.97\textwidth]{mysql-time-smear-plot-Equal}
  %\includegraphics[width=.97\textwidth]{small-mysql-time-smear-plot-Equal}
  \includegraphics[width=.97\textwidth]{figures/mysql-timeline}
  \caption{MySQL 3.23: NFRs over time. Topic frequency relative to that quality is mapped to alpha (transparency) value.}
  \label{fig:mysql}
\end{figure*}
